---
title: "Retail Analysis-Assignment"
author: "Anurag Agrawal"
date: "04/06/2021"
output: html_document
output: pdf_document
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```




```{r}

install.packages("dplyr")

install.packages("ggplot2")

library(dplyr)
library(ggplot2)

print(getwd())

Customer <- read.csv("Customer.csv")

prod_cat_info <- read.csv("prod_cat_info.csv")

Transactions <- read.csv("Transactions.csv")

print(Customer)


```

1. Merge the datasets Customers, Product Hierarchy and Transactions as
  Customer_Final. Ensure to keep all customers who have done transactions with us 
  and select the join type accordingly.
    a. Use the base merge()
    b. Dplyr merge functions
    
```{r}

##  a.Use the base merge()


Result=merge(x=Customer, y=Transactions, by.x = "customer_Id",by.y = "cust_id",)

print(Result)

Customer_Final=merge(x=prod_cat_info, y=Result, by.x="prod_sub_cat_code", by.y ="prod_subcat_code",)

print(Customer_Final)



##  b.Dplyr merge functions
trans_cust_df2 <- left_join(Transactions,
                            Customer,
                            by = c("cust_id" = "customer_Id"))


Customer_Final <- left_join(
  Transactions,
  prod_cat_info,
  by = c("prod_cat_code" = "prod_cat_code",
         "prod_subcat_code" = "prod_sub_cat_code")
)

cat('Dimensions of dataframe obtained through dplyr(): ', dim(Customer_Final))



```


2. Prepare a summary report for the merged data set.
  a. Get the column names and their corresponding data types
  b. Top/Bottom 10 observations
  c. “Five-number summary” for continuous variables (min, Q1, median,Q3 and max)
  d. Frequency tables for all the categorical variables

```{r}
## a. Get the column names and their corresponding data types

column_names <- colnames(Customer_Final)

print(column_names)

for (name in column_names) {
  print(name)
  print(class(Customer_Final[,name]))
}

## b.Top/Bottom 10 observations


head(Customer_Final,n=10)
tail(Customer_Final,n=10)

## c. “Five-number summary” for continuous variables (min, Q1, median,Q3 and max)

for (name in column_names) {
  if(class(Customer_Final[,name]) == "integer"){
    print(name)
    print(summary(Customer_Final[,name]))
  }

  }

##
Customer_Final$dtypes
Customer_Final$loc[Customer_Final$dtypes=="object"]$summary
table(Customer_Final$prod_subcat_code)
table(Customer_Final$prod_cat_code)
table(Customer_Final$Store_type)
table(Customer_Final$Gender)
table(Customer_Final$city_code)
table(Customer_Final$prod_cat)
table(Customer_Final$prod_subcat)
```


3. Generate histograms for all continuous variables and frequency bars for categorical
    variables.


```{r}

vecc <- vector()
for (name in column_names) {
  if(class(Customer_Final[,name]) == "integer"){
    vecc <- c(vecc,name)
  }
}
print(vecc)

Continues_var_dataset <- dplyr::select(Customer_Final,vecc)
print(Continues_var_dataset)

histoplot = ggplot2::ggplot(Continues_var_dataset, aes(x=Qty)) + 
  geom_histogram() + 
  xlab("qty") + 
  ylab("qty") + ggtitle("XXX")


plot(histoplot)

```

4. Calculate the following information using the merged dataset :
  a. Time period of the available transaction data
  b. Count of transactions where the total amount of transaction was negative

```{r}
##   a. Time period of the available transaction data

#boxplot(Customer_Final$tran_date)


##   b. Count of transactions where the total amount of transaction was negative

Continues_var_dataset[Continues_var_dataset$Qty <= 0, ]

```

5. Analyze which product categories are more popular among females vs malecustomers.

```{r}
# prod_cat_code.y

group_Product =group_by(Customer_Final,prod_cat_code.y)
print(group_Product)

max_product_table <- summarise(
  group_Product,
  Sum = sum(Qty)
)
print(max_product_table)

arrange(max_product_table, desc(Sum))

# 5th Product code is popular

```



6. Which City code has the maximum customers and what was thepercentage of customers
    from that city?
    
```{r}


group_city_code =group_by(Customer_Final,city_code)
print(group_city_code)

max_product_table <- summarise(
  group_city_code,
  Count = n_distinct(customer_Id)
)
print(max_product_table)

arrange(max_product_table, desc(Count))



```
    

7. Which store type sells the maximum products by value and by quantity?

```{r}

#   Rate  total_amt Store_type

group_Store_type =group_by(Customer_Final,Store_type)
print(group_Store_type)

max_product_by_value <- summarise(
  group_Store_type,
  p_sum = sum(Rate),
  total_sum = sum(total_amt)
)
print(max_product_by_value)

arrange(max_product_by_value, desc(p_sum) ,desc(total_sum)  )


```


8. What was the total amount earned from the "Electronics" and "Clothing"categories from
    Flagship Stores?
    
```{r}

x_cat <- filter(Customer_Final,prod_cat %in% 
              c("Electronics","Clothing")) 
x <- filter(x_cat,Store_type == "Flagship store")
sum(x$total_amt)


```
    

9. What was the total amount earned from "Male" customers under the"Electronics" 
    category?
    
```{r}
Customer_Final

s=filter(Customer_Final, Gender == 'M' & prod_cat=="Electronics")
summarise(
  s,
  total=sum(total_amt)
)
```
    

10. How many customers have more than 10 unique transactions, afterremoving all 
    transactions which have any negative amounts?
    
```{r}

sd<- data.frame(filter(Customer_Final,total_amt > 0 ))
trans_count <- group_by(sd,cust_id)
y<- summarise(trans_count, total_transaction_id = n_distinct(transaction_id))
y[y$total_transaction_id >10,]

```
    


11. For all customers aged between 25 - 35, find out:
      a. What was the total amount spent for “Electronics” and “Books”product
          categories?
      b. What was the total amount spent by these customers between 1stJan, 2014 to 1st 
          Mar, 2014?

```{r}
sum<- data.frame(filter(Customer_Final, prod_cat =="Electronics" | prod_cat == "Books"))
sum(sum$total_amt)
```
```{r}
##b
startDate =as.Date("01-01-2014")
endDate =as.Date("01-03-2014")
Customer_Final[Customer_Final$tran_date > startDate & Customer_Final$tran_date < endDate,]

filter((Customer_Final$tran_date > startDate) & (Customer_Final$tran_date < endDate ))
Final= mutate(Customer_Final, tran_date < startDate & tran_date >endDate,)
print(Final)
Final= Customer_Final[Customer_Final$`tran_date > startDate & tran_date < endDate`,]
print(Final)
```











